The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-12 article.tex
Fixed formatting in Table 1

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{1in}{ Input } & \multirow{2}{1in}{ Mass tolerance ($\pm$ Da) } & \multicolumn{3}{c}{ \# of generated formulas } & \multicolumn{3}{c}{ Runtime (s) } \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	10,000 small masses & 0.001 & 616,846 & 616,846 & 616,843 & 669 & 168 & \textbf{41} \\
	10,000 small masses & 0.01 & 6,163,303 & 6,163,302 & 6,163,326 & 689 & 501 & \textbf{212} \\
	20 large masses & 0.001 & 4,912,939 & 4,912,939 & 4,912,904 & 26,370 & 1,292 & \textbf{177} \\
	20 large masses & 0.01 & 49,128,811 & 49,128,810 & 49,128,815 & 26,587 & 3,406 & \textbf{1,580} \\
    \end{tabular}
    \end{minipage}

>>>>

    \begin{minipage}{1\textwidth}
    \centering
    \begin{tabular}{llllllll}
	\multirow{2}{1in}{Input} & \multirow{2}{1in}{Mass tolerance ($\pm$~Da)} & \multicolumn{3}{c}{\# of generated formulas} & \multicolumn{3}{c}{Runtime (s)} \\
	& & HR2 & PFG & CDK & HR2 & PFG & CDK \\
	10,000 small masses & 0.001 & 616,846 & 616,846 & 616,843 & 669 & 168 & \textbf{41} \\
	10,000 small masses & 0.01 & 6,163,303 & 6,163,302 & 6,163,326 & 689 & 501 & \textbf{212} \\
	20 large masses & 0.001 & 4,912,939 & 4,912,939 & 4,912,904 & 26,370 & 1,292 & \textbf{177} \\
	20 large masses & 0.01 & 49,128,811 & 49,128,810 & 49,128,815 & 26,587 & 3,406 & \textbf{1,580} \\
    \end{tabular}
    \end{minipage}
